---
title       : Data Product Presentation
subtitle    :  Exploring Random Forests
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## The Assignment

1. Design a Simple Data Product using Shiny / R
2. Set Up a Presentation of the project

--- .class #id 

## Presentation of the Project

- Based on the IRIS data set
- Uses the `party` Package and its variant of Random Forests
- The User is allowed to set the number of trees in the forest
- The User can select any tree in the Forest and the tree is displayed graphically
- The User can enter Measures of an Iris and the predicted species is printed out.

### References

David Meyer, Achim Zeileis, and Kurt Hornik (2006). The Strucplot Framework: Visualizing Multi-Way Contingency Tables with vcd. Journal of Statistical Software, 17(3).

--- .class #id

## The `party` Package and `cforest` Function

```{r}
library(datasets)
library(party)
```{r,warnings=FALSE, results="hide"}
  cf <- cforest(Species ~ ., data = iris, control=cforest_unbiased(ntree=12, mtry=4)) 
  pt <- party:::prettytree(cf@ensemble[[1]], names(cf@data@get("input"))) 
  nt <- new("BinaryTree") 
  nt@tree <- pt 
  nt@data <- cf@data 
  nt@responses <- cf@responses 


```

--- .class #id

## Example of a Tree for ntree=12, mtry=4

```{r, echo=FALSE, fig.height=6, fig.width=12}
plot(nt)
```

